Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-20 paper/ms.tex
Incorporate GB suggestions (part 2)
Co-authored-by: Gaspar Bakos <gbakos@astro.princeton.edu>

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f2a.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with gray crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Zoomed
    windows of individual transits.  Gray lines are the best-fit
    transit model, which includes a local quadratic trend in each
    window.  {\it Bottom}: Phase-folded TESS transit. Gray points are
    2-minute PDCSAP flux measurements with the local spot-induced
    variation removed.  Black points are binned to 6-minute intervals.
    The black error-bar shows the median uncertainty for the black
    points.  The gray line is the best-fit model to the TESS
    data. 
		\label{fig:tessphot}
	}
\end{figure*}

@@

We measured the rotation period from the TESS PDCSAP light curve using the
Lomb-Scargle periodogram implemented in \texttt{astropy}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
We fitted the light curve without masking out the transits or flares,
as these represent a small fraction of the overall time series.  To
derive the uncertainty on the best period, we fitted a Gaussian to the
dominant peak, after first ensuring that we had oversampled the
initial frequency grid.  This gave a rotation period of $P_{\rm rot} =
2.987 \pm 0.056\,{\rm d}$ when allowing for a single Fourier terms in
the periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$
when allowing for two Fourier terms.  As the second model provides a
better fit to the data, we adopt the second measurement.

@@

For the TESS PDCSAP light curve, we first eliminated points that had
quality flags corresponding to any of bits $\{3, 4, 6, 8, 11, 12\}$.
This excluded cadences affected by coarse spacecraft pointing,
reaction wheel desaturation events, manual flags, cosmic ray hits, and
straylight from the Earth or Moon being present.  Inspecting the data,
we also manually excluded the two flares shown in
Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows
of $\pm 7\,{\rm hr}$ centered on each transit.

>>>>

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f2a.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with gray crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    transits.  Gray lines are the best-fit transit model, which
    includes a local quadratic trend in each window. Gray points are
    2-minute \texttt{PDCSAP} flux measurements, black points are binned to
    15-minute intervals.  {\it Bottom}: Phase-folded TESS transit.
    Gray points are 2-minute measurements with the local spot-induced
    variation removed.  Black points are binned to 6-minute intervals.
    The black error-bar shows the median uncertainty for the black
    points.  The gray line shows the best-fit model to the TESS data. 
		\label{fig:tessphot}
	}
\end{figure*}

@@

We measured the rotation period from the TESS \texttt{PDCSAP} light curve using the
Lomb-Scargle periodogram implemented in \texttt{astropy}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
We fitted the light curve without masking out the transits or flares,
as these represent a small fraction of the overall time series.  To
derive the uncertainty on the best period, we fitted a Gaussian to the
dominant peak, after first ensuring that we had oversampled the
initial frequency grid.  This gave a rotation period of $P_{\rm rot} =
2.987 \pm 0.056\,{\rm d}$ when allowing for a single Fourier terms in
the periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$
when allowing for two Fourier terms.  As the second model provides a
better fit to the data, we adopt the second measurement.

@@

For the TESS \texttt{PDCSAP} light curve, we first eliminated points that had
quality flags corresponding to any of bits $\{3, 4, 6, 8, 11, 12\}$.
This excluded cadences affected by coarse spacecraft pointing,
reaction wheel desaturation events, manual flags, cosmic ray hits, and
straylight from the Earth or Moon being present.  Inspecting the data,
we also manually excluded the two flares shown in
Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows
of $\pm 7\,{\rm hr}$ centered on each transit.
